Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-03-17 Paper/paper.tex
Fixed ABHB to ABUHB

The main proposition of the work requested by the ABHB was to develop a mathematical model of bed occupancies at the CCUs at RG and NH.
After an initial analysis of the data, behavioural aspects became apparent; for example, delaying patients discharge if there was no pressure on CCU beds, or admitting fewer patients if bed occupancy levels were high.
As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy \cite{Komenda2013}.
This state dependent model was applied to both NH and RG separately.
It is however obvious that the actions of one CCU impact on the other CCU, as diversion of patients from one CCU to the other sometimes occurs.
A pictorial representation of the situation is given in Figure \ref{diagramofdiversion}.

@@

This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close as possible to a certain target.
As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABHB, long term threshold policies are a realistic consideration.

@@

\begin{itemize}
    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{naor1969regulation, shone2013comparisons});
    \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
    \item The restriction to pure strategies is influenced by discussions with ABHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.  However, allowing for mixed strategies could also be of interest.
\end{itemize}

>>>>

The main proposition of the work requested by the ABUHB was to develop a mathematical model of bed occupancies at the CCUs at RG and NH.
After an initial analysis of the data, behavioural aspects became apparent; for example, delaying patients discharge if there was no pressure on CCU beds, or admitting fewer patients if bed occupancy levels were high.
As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy \cite{Komenda2013}.
This state dependent model was applied to both NH and RG separately.
It is however obvious that the actions of one CCU impact on the other CCU, as diversion of patients from one CCU to the other sometimes occurs.
A pictorial representation of the situation is given in Figure \ref{diagramofdiversion}.

@@

This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close as possible to a certain target.
As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABUHB, long term threshold policies are a realistic consideration.

@@

\begin{itemize}
    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{naor1969regulation, shone2013comparisons});
    \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
    \item The restriction to pure strategies is influenced by discussions with ABUHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.  However, allowing for mixed strategies could also be of interest.
\end{itemize}
